%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX) XD
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}
  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=black, colorlinks=false}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}
\usepackage{listings}
\usepackage{tikz}
\usepackage{3dplot}
\usepackage{tabularx}
\usepackage{lipsum}
\usetikzlibrary{plotmarks}
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usepackage{eurosym}      %<-- For EURO symbol 
\usepackage{filecontents} 
\lstset{basicstyle=\ttfamily,
	showstringspaces=false,
	commentstyle=\color{red},
	keywordstyle=\color{blue}
}
\usepackage{url}

\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{comment}
\usepackage{pifont}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{listings}
\usepackage{afterpage}
%\newcommand{\todo}[1]{{\sl\color{red}$\mathcal{TODO}$: #1}}

\usepackage{spverbatim}
\usepackage{fancyvrb}
\fvset{fontsize=\footnotesize}
\let\verb\Verb

\usepackage{paralist}
\newcolumntype{C}[1]{>{\centering}m{#1}}
\newcommand{\prop}[1]{{\verb|#1|}}

\newcommand{\wikidata}{{Sentiment Analysis}\xspace}
\newcommand{\dbpedia}{{DBpedia}\xspace}
\newcommand{\DW}{{\scshape DBw}\xspace}
\newcommand{\rdf}{{RDF}\xspace}

\renewcommand*{\sectionautorefname}{Section}
\renewcommand*{\subsectionautorefname}{Section}
\renewcommand*{\subsubsectionautorefname}{Section}
\newcommand\blankpage{%
	\null
	\thispagestyle{empty}%
	\addtocounter{page}{-1}%
	\newpage}

\usepackage{fancyhdr}
%% ----------------------------------------------------------------
\begin{document}

\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {Entity Based Sentiment Classifier for Social Media Analysis}
\authors  {\texorpdfstring
            {{Cristobal Leiva}}
            {Cristobal Leiva}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {Machine Learning, SVM, Sentiment Analysis, NLP, IR}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

% \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics


I, Cristobal Leiva, declare that this thesis titled, 'Entity based Sentiment Classifier for Social Media Analysis' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\end{itemize}

Cristobal Leiva
  
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%--------------------------------------------------------------

%% ----------------------------------------------------------------
% The "Quote Page"
\pagestyle{empty}  % No headers or footers for the following pages

\null\vfill
% Now comes the "Funny Quote", written in italics
\textit{"Achievement of your happiness is the only moral purpose of your life, and that happiness, not pain or mindless self-indulgence, is the proof of your moral integrity, since it is the proof and the result of your loyalty to the achievement of your values."}

\begin{flushright}
	Ayn Rand (1905-1982), American philosopher.
\end{flushright}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage  %Quote page ended, start a new page
%% ----------------------------------------------------------------

% The Acknowledgements page, for thanking everyone
\clearpage  % End of the Acknowledgements
\afterpage{\blankpage}
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
%\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
%\lhead{\emph{List of Figures}}  % Set the left side page header to "List of Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
%\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
%\lhead{\emph{List of Listings}}  % Set the left side page header to "List of Listings"
%\lstlistoflistings  % Write out the List of Listings

%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering


% The Abstract Page
%\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
	% \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
	
	
	Having a notion of people’s opinions has always been an essential asset for the decision-making processes in many business models. Therefore, the popularity of sentiment analysis of social media content has being growing rapidly in the last years. However, state-of-the-art sentiment classification approaches lack the capability of performing entity-based classification to identify opinion expressions targeting a specific term, word or entity. In this thesis, this particular problem of entity-based sentiment classification is addressed. 
	
	Combining machine learning and natural language processing methods, the solution proposed in this project uses several sentiment analysis techniques such as Named Entity Recognition (NER), POS tagging, feature vector generation, bag-of-words model and others. These are required to train a Support Vector Machine that classifies tweets (from Twitter) as positive, negative or neutral based on sentiments expressed toward a given target entity (company, person or product). Taking into account real-time sentiment analysis systems, presented solution is developed as a high-performance classifier capable of coping with real-time processing environments. The completeness and effectiveness of this approach is affirmed by quality evaluations and performance tests. 

	
	%Although web resources provide structured data we argue that our integration effort can be beneficial for the end-user.
	\keywords{NLP, IR, Sentiment Analysis, NER, SVM}
	
}
\clearpage  % Abstract ended, start a new page
 %% ----------------------------------------------------------------
% The Acknowledgements page, for thanking everyone
\acknowledgements{
	% \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
	
	It delights me immensely to finally present this thesis to the Department of Computer Science at the University of Bonn, for the partial fulfilment of the Master of Science in Informatik. I would like to thank Professor Dr. S\"oren Auer for his constant support and open arms to accept my thesis proposal. This was a fantastic opportunity and I am fully satisfied with the treatment received by the department and university. I also want to thank Dr. Simon Scerri for supervise this thesis project and always be supportive even in the most difficult circumstances. 
	
	Finally, my sincere gratitude is towards my family and friends who were always there for me. My beloved future wife who did everything she could to keep me on track and focus on our goals. 
	My mother, who I own basically my entire life and achievements. You are the best mother anyone could ever have. Thank you mom! Thank you all!
	
}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{Chapters/Chapter1} % Introduction

\input{Chapters/Chapter2} % Background

\input{Chapters/Chapter3} % Smart Semantic Service for CSP,India

\input{Chapters/Chapter4}  % Ontology re-use

\input{Chapters/Chapter5} % Smart Service in use

\input{Chapters/Chapter6} % Conclusions and Future Work

%% ----------------------------------------------------------------

% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

%\input{Appendices/AppendixA}	% Appendix Title

%\input{Appendices/Appendix} % Appendix Title

%\input{Appendices/AppendixC} % Appendix Title

\input{Appendices/Appendix} % Appendix Title


\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% -------------------------------------------------------------- ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{literature}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------